PANCHANGE_data_preprocessing

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
added coping phq data sets

```{r coping glad gad head}
head(coping.gad.raw.id)
```

@@

Calculate sum score for PCL-6 retro
```{r coping pcl sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_retro <- c(1,1,1,1,1,1)

@@

PCL missingness (NAs per person)

@@

```{r coping glad pcl head}
head(coping.pcl.raw.id)
```

@@

# glad COPING phq

```{r coping glad phq cols}
coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_coping_glad.rds"))
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
```

@@

@@

@@

>>>>

## Inspection
```{r coping glad gad head}
head(coping.gad.raw.id)
```

@@

## Sum scores
Calculate sum score for PCL-6 retro
```{r coping pcl sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_retro <- c(1,1,1,1,1,1)

@@

## Missingness
PCL missingness (NAs per person)

@@

## Inspection
```{r coping glad pcl head}
head(coping.pcl.raw.id)
```

@@

# COPING: PHQ

## GLAD
```{r coping glad phq cols}
coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_coping_glad.rds"))
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
```

@@

## EDGI
```{r coping edgi phq cols}
coping.edgi.phq.raw <- readRDS(file = paste0(data.raw_path, "/edgi/phq_coping_edgi.rds"))
dim(coping.edgi.phq.raw)
colnames(coping.edgi.phq.raw)
```

```{r coping edgi phq summary labels}
summarytools::dfSummary(
  coping.edgi.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```

Will need to double check these namings once we have the new cleaned data -- KT. 
```{r coping edgi phq cleaning}
coping.edgi.phq.raw.id <- coping.edgi.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)
  ) %>%
  select(
    Sample, # Sample
    ID, # ID
    phq.problems_made_difficult_care,
    phq.pandemic_felt_feelings,
    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ EDGI prepandemic
    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ EDGI prepandemic
    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ EDGI prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ EDGI prepandemic
    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.edgi.phq.raw.id)
# Inspect colnames
colnames(coping.edgi.phq.raw.id)
#Differences
dim(coping.edgi.phq.raw)[1]-dim(coping.edgi.phq.raw.id)[1]
```

## NBR
```{r coping nbr phq cols}
coping.nbr.phq.raw <- readRDS(file = paste0(data.raw_path, "/nbr/phq_coping_nbr.rds"))
dim(coping.nbr.phq.raw)
colnames(coping.nbr.phq.raw)
```

```{r coping nbr phq summary labels}
summarytools::dfSummary(
  coping.nbr.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```

Will need to double check these namings once we have the new cleaned data -- KT. 
```{r coping nbr phq cleaning}
coping.nbr.phq.raw.id <- coping.nbr.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)
  ) %>%
  select(
    Sample, # Sample
    ID, # ID
    phq.problems_made_difficult_care,
    phq.pandemic_felt_feelings,
    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ NBR prepandemic
    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ NBR prepandemic
    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ NBR prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ NBR prepandemic
    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.nbr.phq.raw.id)
# Inspect colnames
colnames(coping.nbr.phq.raw.id)
#Differences
dim(coping.nbr.phq.raw)[1]-dim(coping.nbr.phq.raw.id)[1]
```

## RAMP
```{r coping ramp phq cols}
coping.ramp.phq.raw <- readRDS(file = paste0(data.raw_path, "/ramp/phq_coping_ramp.rds"))
dim(coping.ramp.phq.raw)
colnames(coping.ramp.phq.raw)
```

```{r coping ramp phq summary labels}
summarytools::dfSummary(
  coping.ramp.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```

Will need to double check these namings once we have the new cleaned data -- KT. 
```{r coping ramp phq cleaning}
coping.ramp.phq.raw.id <- coping.ramp.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)
  ) %>%
  select(
    Sample, # Sample
    ID, # ID
    phq.problems_made_difficult_care,
    phq.pandemic_felt_feelings,
    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ RAMP prepandemic
    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ RAMP prepandemic
    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ RAMP prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ RAMP prepandemic
    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.ramp.phq.raw.id)
# Inspect colnames
colnames(coping.ramp.phq.raw.id)
#Differences
dim(coping.ramp.phq.raw)[1]-dim(coping.ramp.phq.raw.id)[1]
```

## Sum scores

@@

# Missingness

@@

## Inspection
